---
title: "The Sentimen Evaluation of Customer Review in Las Vegas City Restaurants"
author: "Pozy Pak Ya"
date: "October 22, 2015"
output:
  pdf_document: null
  html_document: null
  word_document:
    fig_caption: yes
fontsize: 10pt
documentclass: article
classoption: a4paper
---

# Abstract 

*From recent trends, many online reviews include a numerical or star rating that quantifies the satisfaction of the reviewer's experience. However, an
objective mapping of this quantitative rating to the reviewer's textual description does not yet exist. In this paper, we explore models ranging from support vector machines to learning word vectors that capture the sentiment information of individual words in relation to ratings of an entire document. We use Yelp reviews for restaurants near particular universities to predict corresponding star ratings per review.*

# Keywords
Urban design, social media, geo-location, lexicographic analysis, sentiment analysis

```{r , echo=FALSE , message=F, warning=F}
assign("last.warning", NULL, envir = baseenv())
suppressWarnings(suppressMessages(library(ggplot2)))
suppressWarnings(suppressMessages(library(xlsx)))
suppressWarnings(suppressMessages(library(sentiment)))
suppressWarnings(suppressMessages(library(wordcloud)))
suppressWarnings(suppressMessages(library(RODBC)))
suppressWarnings(suppressMessages(library(pander)))
suppressWarnings(suppressMessages(library(ggmap)))
suppressWarnings(suppressMessages(library(RColorBrewer)))
suppressWarnings(suppressMessages(library(Rstem)))
suppressWarnings(suppressMessages(library(tm)))
suppressWarnings(suppressMessages(library(NLP)))
suppressWarnings(suppressMessages(library(rmarkdown)))
suppressWarnings(suppressMessages(library(gridExtra)))
suppressWarnings(suppressMessages(library(Rmisc)))
suppressWarnings(suppressMessages(library(png)))
suppressWarnings(suppressMessages(library(grid)))
suppressWarnings(suppressMessages(library(igraph)))
suppressWarnings(suppressMessages(library(RPMG)))
suppressWarnings(suppressMessages(library(Hmisc)))

```

# Introduction

The evaluation is about the sentiment analysis over the review and stars rating restaurant in the Last Vegas city.. The YELP dataset is very resourceful which provides the valuation criteria over 61,184  unique records for `business` , 1,569,264 records for `review` and 495,107 records for the `tips`. Two tables have been discarded for now ,which is `user` details and the `check-in` information.The GPS longitude and latitude available inside the `business` dataset which provides very useful information about its geolocation. The star value gives the feedback from the customer which might be `positive` , `negative` or `neutral`.
The findings offer exemplary `big data` analysis methods as the evaluation of socially mediated urban space associated with the pattern classification of textual information inside the `reviews` and `tips` in relation with `business` dataset.

```{r , echo=FALSE }
df <- read.csv("a.csv")
#df <-
#sqlQuery(
#conn, "select  review_count , categories , city from business group by review_count , categories , city order by review_count desc")
```

`Las Vegas` City is the top 5 locations with the most review counted as follows :-


```{r echo=FALSE}
panderOptions("digits", 2)
pander(head(df),caption = "Top 5 City Reviews and Categories")

```

In more details , `Mon Ami Gabi` is the top of 5 `Las Vegas` restaurant by the most reviewed counted as follows :-

```{r echo=FALSE , fig.height=3 , fig.align='center' , message=F, warning=F}
df <- read.csv("d.csv") 
panderOptions("digits", 2)
pander(head(df),caption = "Las Vegas City Restaurant")

```

The summary of the `joined` dataset as follows  :-

```{r , echo=FALSE }
df <- read.csv("b.csv")
df1 <- df
df1$name <- NULL
df1$city <- NULL
df1$categories <- NULL
df1$cc <- NULL
df1$gog <- NULL
df1$alcohol <- NULL
#summary(df1$review_count)


panderOptions("digits", 2)
pander(summary(df1$review_count),caption = "Summary of Las Vegas City Restaurant No. Of Review")

```

To reduce the size of the sample , average size of numbers of message is the minimal size which is around 390. And the numbers of group identified around 1000 

From the summary show that the Median is `26` and we choose `26` as the minimal sample for this evaluation. The median better than mean because of it is a symmetrical statistic and more resistant to errors.

# Methods and Data 

The dataset is obtained from the YELP website (http://www.yelp.com/dataset_challenge) and extracted. The format for the dataset is in `JSON` . JSON need special techniques to parse and read from it. Apache Hive is the best component which is capable read this format . Since the dataset required to have a good machine in term of CPU and memory , we push this dataset to work inside Hadoop which Map-Reduce can be used as the framework for the filtering and cleaning over large size of the dataset. Hive is compatible to use scripting parameter similar to SQL and this is very suitable for speed up the entire development work. Hive also support for the complex data type and  `STRUCT` is used to handle the JSON complex type for the table creation inside Hive .

For the basic analysis , this evaluation requires a fair amount time to know about the dataset abd performaing exploratory analysis. But, now we only focus on the textual information which mostly inside the `review` and `tips` dataset in conjuction with the `business` and `user` information. This will tackle some of the questions such as :-

* What is the emotion type that might contain inside the review and tips messages ?
* What is the most frequent words or terms inside it ?

Below is the answers for the questions above . Top common words inside the review is regarding the `good food , good places and also a good services `. Reviewers whom visits seems very happy about the quality of food , services and places restaurant in Las Vegas. Most of the comments seems positively accepts it.

```{r echo=FALSE ,  fig.align='center' ,   fig.height=4 , fig.width=8 ,  message=F, warning=F}
df_review <- read.csv("f.csv")
df_review <- as.data.frame(tolower(df_review$review))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:digit:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:punct:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="@\\w+",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="^\\s+|\\s+$",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[ \t]{2,}",replacement=""))
names(df_review) = "review"
#words_list = strsplit(as.character(df_review$review), " ")

mach_corpus = Corpus(VectorSource(df_review$review))

# create document term matrix applying some transformations
tdm = TermDocumentMatrix(
mach_corpus,
control = list(
removePunctuation = TRUE,
stopwords = c(stopwords("english")),
removeNumbers = TRUE, tolower = TRUE
)
)
m <- as.matrix(tdm)
v <- sort(rowSums(m), decreasing = TRUE)

class_emo = classify_emotion(df_review$review[1:10], algorithm = "bayes", prior =
1.0)
emotion = class_emo[,7]
emotion[is.na(emotion)] = "unknown"
class_pol = classify_polarity(df_review$review[1:10], algorithm = "bayes")
# get polarity best fit
polarity = class_pol[,4]
pct <-
round(table(as.data.frame(class_pol)$BEST_FIT) / sum(table(as.data.frame(class_pol)$BEST_FIT)) *
100)
lbl <- as.data.frame(class_pol)$BEST_FIT

par(mfrow = c(1,2))
barplot(
head(v, 10), border = NA, las = 2, main = "Top 10 most frequent terms", cex.main =
1 , col = topo.colors(2)
)
pie(
table(as.data.frame(class_pol)$BEST_FIT) / length(as.data.frame(class_pol)$BEST_FIT), labels = paste(capitalize( as.character(lbl)),'(',pct,'%)'), main =
"Emotion Polarity of Review Messages "
)

```

* Food Selection Discovery

To discover what types of food been reviewed most by the reviewer , `word-cloud` plot is used to splot the word frequencies. Since to have the food-list dataset is hard to compile due to there is a lot of food around the world , by plotting it into word cloud we easily can identify manually pick the food that we recognize as follows :- 

```{r echo=FALSE , fig.height=3 , fig.width=3 , fig.align='center' , message=F, warning=F}
df_review <- read.csv("f.csv")
df_review <- df_review$review
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:digit:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:punct:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="@\\w+",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="^\\s+|\\s+$",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[ \t]{2,}",replacement=""))
names(df_review) = "review"

# create a corpus
mach_corpus = Corpus(VectorSource(df_review))

# create document term matrix applying some transformations
tdm = TermDocumentMatrix(mach_corpus,
   control = list(removePunctuation = TRUE,
   stopwords = c("machine", "learning", stopwords("english")),
   removeNumbers = TRUE, tolower = TRUE))

# define tdm as matrix
m = as.matrix(tdm)
# get word counts in decreasing order
word_freqs = sort(rowSums(m), decreasing=TRUE) 
# create a data frame with words and their frequencies
dm = data.frame(word=names(word_freqs), freq=word_freqs)

suppressWarnings(suppressMessages(wordcloud(dm$word[1:500], dm$freq[1:500], random.order=FALSE, colors=brewer.pal(8, "Dark2"))))
```

From the above information we can make the assumption that the result shows the common food that always mention by the reviewer are `chicken` , `sushi` , `burger` , `pizza` , `cheese` , `salad` , `rice` and `sauce`. We use this list as the base of common food can be relate with the emotion of the reviewer. List of emotion that can be identified , such as `friendly` , `best` , `well` , and `nice` .
So, we entrusted with the food type listed and we want to have some idea what are their possible relationship . To achieve this , is to use the `word-graph` techniques for 8 groups of food  and the result as follows :-

```{r echo=FALSE , fig.height=5 , fig.align='center' , message=F, warning=F}

df_review <- read.csv("g.csv",header = TRUE)
df_review <- as.data.frame(tolower(df_review$review))
names(df_review) = "review"
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:digit:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:punct:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="@\\w+",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="^\\s+|\\s+$",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[ \t]{2,}",replacement=""))
#df_review <-as.data.frame(sapply(df_review,gsub,pattern="\\:",replacement=""))
#df_review <- as.data.frame(df_review$review[1:10])
names(df_review) = "review"

corpus = Corpus(VectorSource(df_review))
skipwords = c(stopwords("english"), 
   "chicken", "sushi", "burger", "pizza", "cheese", "salad", "rice", "sauce")
corpus = tm_map(corpus, removeWords, skipwords)
# term-document matrix
tdm = TermDocumentMatrix(corpus)
#tdm <- removeSparseTerms(tdm, sparse= 0.7)
# convert tdm to matrix
m = as.matrix(tdm)
# word counts
wc = rowSums(m)

# get those words above the 3rd quantile
lim = quantile(wc, probs=0.5)
good = m[wc > lim,]

# adjacency matrix
M = good %*% t(good)

# set zeroes in diagonal
diag(M) = 0

# graph
g = graph.adjacency(M, weighted=TRUE, mode="undirected",add.rownames=TRUE)
# layout
glay = layout.fruchterman.reingold(g)

# let's superimpose a cluster structure with k-means clustering
kmg = kmeans(M, centers=8)
gk = kmg$cluster

# create nice colors for each cluster
gbrew = c("red", brewer.pal(8, "Dark2"))
gpal = rgb2hsv(col2rgb(gbrew))
gcols = rep("", length(gk))
for (k in 1:8) {
gcols[gk == k] = hsv(gpal[1,k], gpal[2,k], gpal[3,k], alpha=0.5)
}

# prepare ingredients for plot
V(g)$size = 10
V(g)$label = V(g)$name
V(g)$degree = degree(g)
#V(g)$label.cex = 1.5 * log10(V(g)$degree)
V(g)$label.color = hsv(0, 0, 0.2, 0.55)
V(g)$frame.color = NA
V(g)$color = gcols
E(g)$color = hsv(0, 0, 0.7, 0.3)

# plot
plot(g, layout=glay)
title("\nLast Vegas Restaurant Food Graph",
col.main="gray40", cex.main=1.5)

chars_per_tweet = sapply(as.vector(df_review$review), nchar)

```

The graph shows that there is a few groups of words which their possible relationship and have the idea of the main term used.

Other interesting findings in this evaluation is to classify the reviewers ratings and the tips provided. The idea is to calculate the sentimen score for each messages so we can know how positive and negative the messages. Below is the formula of the how to calculate the score :-

```
      Score  =  Number of positive words  -  Number of negative words`

```
* If the `score > 0` , the messages has overall `positive` opinion
* If the `score < 0` , the messages has overall `negative` opinion
* If the `score = 0` , the messages has can be consider as `neutral` opinion

The lexicon is in English and the reference for the `positive` and `negative` words is reference from  (https://github.com/SamPortnow/Depression_Prevention_Program/tree/master/bato/assets).



# Results

The results from the all analysis we can summarized by plotting the dispersion of the message size inside the map of Las Vegas restaurant. We the conclusion , we find out that the message is more focus in the area of  `Fountains of Bellagio` along the `S Las Vegas Blvd` road. This road is the main highway in Las Vegas and there is a lot of casinos along it. The illustration below :-

```{r echo=FALSE , fig.height=4 , fig.width=5 , message=F, warning=F}

df <- read.csv("b.csv") 
df1 <- df
df1$name <- NULL
df1$city <- NULL
df1$categories <- NULL
df1$cc <- NULL
df1$gog <- NULL
df1$alcohol <- NULL
#df1$review_count
#df1$longitude <- NULL
#df1$latitude <- NULL
#df1$cc <- as.numeric(as.factor(df1$cc))
#df1$cc[is.na(df1$cc)] <- 0

#df1$gog <- as.numeric(as.factor(df1$gog))
#df1$gog[is.na(df1$gog)] <- 0

#df1$alcohol <- as.numeric(as.factor(df1$alcohol))
#df1$alcohol[is.na(df1$alcohol)] <- 0

#(kc <- kmeans(df1,14)) 
#plot(df1[c("latitude", "longitude")], col=kc$cluster)


mapImageData1 <-
  suppressWarnings(suppressMessages(get_map(
  location = c(lon = mean(df1$longitude), lat = mean(df1$latitude)),
  maptype = "roadmap" , color = "bw",
  zoom = 13
  )))
  lon <- data.frame(df1$longitude)
  lat <- data.frame(df1$latitude)
  f <- data.frame(df1$review_count)
  mydf <- as.data.frame(cbind(lon,lat,f))
  names(mydf) = c("lon","lat","review")
  mapImageData1 <-
  suppressWarnings(suppressMessages(get_map(
  location = c(lon = mean(df1$longitude), lat = mean(df1$latitude)),
  maptype = "roadmap" , color = "bw",
  zoom = 13
  )))

  par(mfrow = c(1,2))
  p <-
  suppressWarnings(ggmap(mapImageData1)) + suppressWarnings(geom_point(data = mydf, aes(
  x = lon,y = lat , color = review ,size = review ,alpha = 0.2
  ))) + ggtitle('Review Size Dispersion by Location') 
  suppressWarnings(p)
  suppressWarnings(p)
  
```
Figure 1 : Venue with greater than 390 review messages

Bagitau list of restaurant yang banyak impact dan types of food yang ada sesama mereka kalau ada relationship

The population is because the location is very strategic and nearest to the airport

Figure 2 : Venue with greater than 390 review messages

* Sentiment Analysis

Positive correlated with the positive emotion words

Figure 3 : Venue with weighted by the numbers of keywords

Sentiment analysis on keyword left 70% of the dataset with neutral sentiment.
Sentiment was found to be 74% positive in nature which corresponds to about 22% of the total sample
In contrast,26% was negative in nature which corresponds to only 8% of the total sample

Figure 4 : Venue with weighted by the numbers of keywords , with positive weight
Figure 5 : Venue with weighted by the numbers of keywords , with negative weight
Figure 6 : Total sentiment classification with positive , negative and neutral
Figure 7 : Cloudwords postive and negative

* Temporal Analysis

Figure 8 : Duration - Negative vs Positive + Neutral
Figure 9 : Comparison by month


4.  Method Used -  Classification , Bayes



Is there any relation between the business type ?


```{r echo=FALSE , fig.height=3 , fig.align='center' , message=F, warning=F}
df <- read.csv("e.csv") 
#suppressWarnings(suppressMessages(odbcClose(conn)))

df_review <- as.data.frame(tolower(df$review))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:digit:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[[:punct:]]",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="@\\w+",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="^\\s+|\\s+$",replacement=""))
df_review <-as.data.frame(sapply(df_review,gsub,pattern="[ \t]{2,}",replacement=""))
names(df_review) = "review"

df_tips <- as.data.frame(tolower(df$tips))
df_tips <-as.data.frame(sapply(df_tips,gsub,pattern="[[:digit:]]",replacement=""))
df_tips <-as.data.frame(sapply(df_tips,gsub,pattern="[[:punct:]]",replacement=""))
df_tips <-as.data.frame(sapply(df_tips,gsub,pattern="@\\w+",replacement=""))
df_tips <-as.data.frame(sapply(df_tips,gsub,pattern="^\\s+|\\s+$",replacement=""))
df_tips <-as.data.frame(sapply(df_tips,gsub,pattern="[ \t]{2,}",replacement=""))
#df_tips = as.data.frame(sapply(df_tips, try.error))
#df_tips = as.data.frame(df_tips[!is.na(df)])
names(df_tips) = "tips"

```

The `HEAD` records for business types , average ratings and the average review count as follows :


```{r echo=FALSE , fig.height=3 , fig.width=9 ,  message=F, warning=F}
#panderOptions("digits", 2)
#pander(head(df),caption = "Las Vegas City Restaurant")

#================================================================================================
# Messages
#================================================================================================

class_emo = classify_emotion(df_review, algorithm="bayes", prior=1.0)
emotion = class_emo[,7]
emotion[is.na(emotion)] = "unknown"
class_pol = classify_polarity(df_review, algorithm="bayes")
# get polarity best fit
polarity = class_pol[,4]

# data frame with results
sent_df = data.frame(text=df_review, emotion=emotion,
polarity=polarity, stringsAsFactors=FALSE)

sent_df = within(sent_df,
  emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))

df_df_review_combined <- cbind(df,sent_df)

emos = levels(factor(sent_df$emotion))
nemo = length(emos)
emo.docs = rep("", nemo)
for (i in 1:nemo)
{
   tmp = df$review[emotion == emos[i]]
   emo.docs[i] = paste(tmp, collapse=" ")
}

# remove stopwords
emo.docs = removeWords(emo.docs, stopwords("english"))
# create corpus
corpus = Corpus(VectorSource(emo.docs))
tdm_review = TermDocumentMatrix(corpus)
tdm_review = as.matrix(tdm_review)
colnames(tdm_review) = emos



a <- ggplot(sent_df, aes(x = emotion)) +
  geom_bar(aes(y = ..count.., fill = emotion)) +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "emotion", y = "# review")+ labs(title =
  "  L.V Review Emotion ")

b <- ggplot(sent_df, aes(x = polarity)) +
  geom_bar(aes(y = ..count.., fill = polarity)) +
  scale_fill_brewer(palette = "RdGy") +
  labs(x = "polarity", y = "# review") + labs(title =
  "  L.V Connotation Polarity")

#par(mfrow = c(1))



```

```{r echo=FALSE , fig.height=3 , fig.width=5 ,  message=F, warning=F}

multiplot(a,b,cols = 2)
suppressWarnings(suppressMessages(comparison.cloud(tdm_review, colors = brewer.pal(nemo, "Dark2"),
   scale = c(1,.5), random.order = FALSE, title.size = 1.5)))

```

Tips

```{r echo=FALSE , fig.height=3 , fig.width=5 ,  message=F, warning=F}
class_emo = classify_emotion(df_tips, algorithm="bayes", prior=1.0)
emotion = class_emo[,7]
emotion[is.na(emotion)] = "unknown"
class_pol = classify_polarity(df_tips, algorithm="bayes")
# get polarity best fit
polarity = class_pol[,4]

# data frame with results
sent_df = data.frame(text=df_tips, emotion=emotion,
polarity=polarity, stringsAsFactors=FALSE)

sent_df = within(sent_df,
  emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))

df_df_tips_combined <- cbind(df,sent_df)

```

Cerita techniques yang dipakai di sini

```{r echo=FALSE , fig.height=3 , fig.width=5 ,  message=F, warning=F}
a <- ggplot(sent_df, aes(x = emotion)) +
  geom_bar(aes(y = ..count.., fill = emotion)) +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "emotion", y = "# tips")+ labs(title =
  "  L.V Tips Emotion ")

b <- ggplot(sent_df, aes(x = polarity)) +
  geom_bar(aes(y = ..count.., fill = polarity)) +
  scale_fill_brewer(palette = "RdGy") +
  labs(x = "polarity", y = "# tips") + labs(title =
  "  L.V Tips Polarity")


emos = levels(factor(sent_df$emotion))
nemo = length(emos)
emo.docs = rep("", nemo)
for (i in 1:nemo)
{
   tmp = df$review[emotion == emos[i]]
   emo.docs[i] = paste(tmp, collapse=" ")
}

# remove stopwords
emo.docs = removeWords(emo.docs, stopwords("english"))
# create corpus
corpus = Corpus(VectorSource(emo.docs))
tdm_tips = TermDocumentMatrix(corpus)
tdm_tips = as.matrix(tdm_tips)
colnames(tdm_tips) = emos

# comparison word cloud

multiplot(a,b,cols = 2)

#png(filename="cloud1.png")
suppressWarnings(suppressMessages(comparison.cloud(tdm_tips, colors = brewer.pal(nemo, "Dark2"),
   scale = c(4,.5), random.order = FALSE, title.size = 1.5)))
#dev.off()

#img <-  readPNG("cloud1.png")

```

# Discussion 




```{r echo=FALSE , fig.height=3 , fig.align='center' , message=F, warning=F}

```

DISCUSSION 
The issue of using such data in a real planning situation raises several significant questions: 1) how to determine the extent of limited demographic information, data frequency, and the privacy concerns of Twitter users, 2) accessing and processing increasingly larger data, and 3) assuring a sample's diversity. In response, we believe that the three analysis techniques described above suggests that: 1) Big Data can become a robust tool, 2) Density can be coupled with temporal patterns to reveal dynamic sentiment monitored city wide offering detailed views of social trends. For issues related to better informed decision making, characterizing urban areas is essential. Through the union of data and location as exemplified in this study, multiple layers of realtime information can be displayed geographically, providing enhanced situational contexts and the deciphering of evolving social narratives. Odendaal (2006) acknowledges this premise, suggesting a growing movement in urban planning to utilize city narratives in the process of understanding place. The paper suggests that public life within digital social networks can tell an exceptionally well documented story.

In our experiment, we mapped the star ratings down to simplified 1 and 0 values, to signify a sharp polarity between positive and negative reviews. Initially, we had hoped to work towards a model that allowed us to make an entirely quantitative star rating measure of a review. We can design our model to better capture this information. We can also include more data by factoring in the three ratings per review provided by
Yelp.

We have presented 3 algorithms chosen for their simplicity of implementation and run time efficiency. The results suggest that our classification-based approach performs better than numeric or ordinal regression approaches. Our next step is to verify these results with the more advanced algorithms outlined below.1. For many numeric regression problems, (boosted) classification trees have shown good performance.2. Several multi-threshold implementations of
Support Vector Ordinal Regression are compared in Chu and Keerthi (2005). While they are more principled than the Perceptron-based PRank, their implementation is significantly more complex. A simpler approach that performs regression using a single classifier extracts extended examples from the original examples (Li and Lin, 2007). 3. Among classification-based approaches, nested binary classifiers have been proposed (Frank and Hall, 2001) to take into account the ordering information, but the prediction procedure based on classifier score difference is ad-hoc.

Textual reviews for different products and services are abundant. Still, when trying to make a buy decision, getting sufficient and reliable information can be a daunting task. In this work, instead of a single overall rating we focus on providing ratings for multiple aspects of the product/service. Since most textual reviews are rarely accompanied by multiple aspect ratings, such ratings must be deduced from predictive models. Several authors in the past have studied this problem using both classification and regression models. In this work we show that even though the aspect rating problem seems like a regression problem, maximum entropy classification models perform the best. Results also show a strong inter-dependence in the way users rate different aspects.

https://sites.google.com/site/miningtwitter/questions/talking-about/given-topic


